Tree size, exposure, and hydraulic traits interactively shape drought response in a temperate broadleaf forest

### 2019-06-10 manuscript/index.Rmd
Added Joseph as author

---
title: "Tree size, exposure, and hydraulic traits interactively shape drought response in a temperate broadleaf forest"
author: "Ian McGregor, Ryan Helcoski, Norbert Kunert, Alan Tepley, Valentine Herrmann, Neil Pederson, Lawren Sack, Krista Anderson-Teixeira"
output: html_document
documentclass: book
bibliography: [book.bib]
biblio-style: apalike
link-citations: yes
github-repo: manuscript/outline
description: "Article for Ian's research during his time in Anderson-Teixeira lab"
---

>>>>

---
title: "Tree size, exposure, and hydraulic traits interactively shape drought response in a temperate broadleaf forest"
author: "Ian McGregor, Ryan Helcoski, Norbert Kunert, Alan Tepley, Valentine Herrmann, Neil Pederson, Lawren Sack, Joseph Zailaa, Krista Anderson-Teixeira"
output: html_document
documentclass: book
bibliography: [book.bib]
biblio-style: apalike
link-citations: yes
github-repo: manuscript/outline
description: "Article for Ian's research during his time in Anderson-Teixeira lab"
---
